\documentclass{article}

\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{ragged2e}
\usepackage[margin=1in]{geometry}

\titleformat{\section}{\filcenter\Large\bfseries\lowercase}{}{0em}{}[\titlerule]

\titleformat{\subsection}[runin]{\bfseries\large}{$\gtrdot$ }{0em}{}

\titleformat{\subsubsection}[runin]{\bfseries}{$\gtrdot$ }{0em}{}
\titlespacing{\subsubsection}{0em}{0em}{.5em}

\titleformat{\paragraph}[runin]{\small}{}{0em}{}
\titlespacing{\paragraph}{0em}{0em}{.5em}

\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries\theauthor}

\vspace{.25em}

(570) 956-9993 $\vert$ benji6090@gmail.com $\vert$ github.com/benlloyd50

\end{center}
}

\begin{document}
\title{Resume}

\author{Benjamin Lloyd}

\maketitle

\section{Education}
\subsubsection{B.S. Computer Science/Software Development \textit{cum laude} \hfill Jan '22 - May '23  } 
\textbf\paragraph{ Kutztown University, Kutztown PA }

\subsubsection{A.S. Computer Science \hfill Aug '20 - Dec '21  } 
\textbf\paragraph{ Luzerne County Community College, Nanticoke, PA }

\section{Technical Skills}

\subsubsection{Programming Languages} C\# + .NET, Javascript, Python, Typescript, C++, Rust, Delphi

\subsubsection{Technologies} Git, Azure, MySQL, SQLite, PostgreSQL, Windows/Linux, JMeter, Neovim,  Unity

\subsubsection{Communications} Agile Scrum, Kanban, Trello, MS Teams, Zoom

\section{Job Experience}
\subsection{Software Developer - Gateway Ticketing Systems} \hfill May '22 - June '24
\paragraph{Gilbertsville, PA}

\begin{itemize}
  \itemsep0em 
  \item Created and maintained automation tests to maximize code coverage and catch bugs before releases. This helped to catch dozens of regressions and new bugs and tests passing improved by 20\%. 
  \item Developed in house apps with C\# and Delphi by working on problems that users regularly faced. Identified common performance bottlenecks and 
  refactored to improve performance by up to 25\%.
  \item Used CI/CD like Jenkins and Azure to test more and ensure less chances of bugs in production.
  \item Collaborated with inter-departmental scrum team to refine project architecture, code organization, and improve task velocity.
\end{itemize}

\subsection{Supervisor/Customer Service Associate - Sheetz} \hfill Jan '19 - May '22
\paragraph{Shoemakersville, PA}
\begin{itemize}
  \itemsep0em 
  \item Led and managed a team of up to 6 individuals, ensuring efficiency and a safe working environment.
  \item Resolved customer inquiries and concerns with a strong focus on customer satisfaction, effectively retaining and growing the customer base.
  \item Conducted training sessions for new team members, fostering a culture of learning and professional growth.
\end{itemize}

\subsection{Math Tutor - Luzerne County Community College Tutoring} \hfill Jan '21 - May '21
\paragraph{Nanticoke, PA}
\begin{itemize}
  \itemsep0em 
  \item Provided one-on-one tutoring for up to 4 students, offering personalized guidance in math courses.
  \item Assisted students in grasping complex mathematical concepts by breaking down topics into simpler explanations.
\end{itemize}

\section{Extracurriculars and Projects}
\begin{itemize}
  \itemsep0em 
  \item[\bfseries YouTube] Creating educational content around learning programming languages for beginners. youtube.com/@Ben\_Lloyd
  \item[\bfseries Game Dev.] Creating games with a variety of technologies such as Unity and Rust to explore unique programming challenges. Participating in Game Jams to focus on scope management and finishing projects.
\end{itemize}

\thispagestyle{empty}
\end{document}

